

```{r}
library(shiny)
library(shinydashboard)
library(leaflet)
library(dplyr)
library(curl)
library(sf)
library(bcmaps)

```



```{r}
municipalities <- municipalities()
municipalities <- (municipalities[(municipalities$ADMIN_AREA_ABBREVIATION == "Victoria"|municipalities$ADMIN_AREA_ABBREVIATION == "Oak Bay" | municipalities$ADMIN_AREA_ABBREVIATION == "Duncan"  |municipalities$ADMIN_AREA_ABBREVIATION ==  "Central Saanich" |  municipalities$ADMIN_AREA_ABBREVIATION =="View Royal" | municipalities$ADMIN_AREA_ABBREVIATION == "North Saanich"| municipalities$ADMIN_AREA_ABBREVIATION == "Colwood"| municipalities$ADMIN_AREA_ABBREVIATION == "Esquimalt" |  municipalities$ADMIN_AREA_ABBREVIATION == "Saanich"|  municipalities$ADMIN_AREA_ABBREVIATION == "Langford"),])
municipalities <- st_transform(municipalities, "+proj=longlat +datum=WGS84")



subdivisions <- census_subdivision()
subdivisions <- (subdivisions[(subdivisions$CENSUS_SUBDIVISION_NAME == "Victoria"),])
subdivisions <- st_transform(subdivisions, "+proj=longlat +datum=WGS84")


district <- regional_districts()
district <- district[(district$ADMIN_AREA_ABBREVIATION == "CAPRD"),]
district <- st_transform(district, "+proj=longlat +datum=WGS84")
```
```{r}
shapes <- read_sf('routes.shp')
city <- read.csv("file.csv")
```

```{r}
header <- dashboardHeader(
  title = "Victoria Transit Map"
)

body <- dashboardBody(
  
   fluidRow(
   
    column(width = 9,
      box(width = NULL, solidHeader = TRUE,
        leafletOutput("map", height = 500)
      ),
      
    ),
    column(width = 3,
      box(width = NULL, status = "warning",
        uiOutput("select_route"),
       
      ),
      box(width = NULL, status = "warning",
        uiOutput("information"),
       
      ),
      
    )
   )
  ) 


 
ui <-  dashboardPage(
  header,
  dashboardSidebar(disable = TRUE),
  body
)

route_shape_fun<-function(route_no){

  shapes[(shapes$Route == route_no),]
  
}


time <-function(route_no){

  
  
  city <- city[(city$route_short_name == route_no),]
  total <- nrow(city)-1
  vic <- 0

  for(i in 1:total){
   if(city$muni[i] == "Victoria"){
    
     vic <- vic+1
     
   }else{
     vic <- vic
   }
   
  }
 
  percentage = round(((vic/total)*100),0)
  
 print(paste("Bus Number",route_no, "spends", percentage, "percent of trip time in Victoria, B.C."))
 
}



server <- function(input, output, session){

   output$select_route <- renderUI({
    route_no <- sort(unique(as.numeric(shapes$Route)))
    
    names(route_no) <- route_no
    
    route_no <- c(All = 0, route_no)
    selectInput("route_no", "Route", choices = route_no, selected = route_no[2])
  })
   
   output$information <- renderUI({
     if(as.numeric(input$route_no != 0)){
       return(time(input$route_no))
     } else{
       print("Please choose specific route no")
     }
    
     
     
   })
   
   
   output$map <-renderLeaflet({
     
    
      map <- leaflet() %>%
       addTiles() %>%
        setView(lng = -123.3656, lat = 48.4284, zoom = 12)
       
       
        map <- addPolylines(map, data = subdivisions, fill = TRUE, fillColor = "Grey", color = "Blue")
        map <- addPolylines(map, data = municipalities, fill = FALSE, color = "Green", label = municipalities$ADMIN_AREA_ABBREVIATION)
        
        
       
        if(as.numeric(input$route_no != 0)){
         
          route_shape <- route_shape_fun(input$route_no)
        
        
          coords <- st_coordinates(route_shape)
        n <-  nrow(coords)
        longstart = coords[1,1]
        latstart = coords[1,2]
      
        longend = coords[n,1]
        latend = coords[n,2]
       content <-time(input$route_no)

        
        map <- addPolylines(map, data = route_shape, color = "Red", label = input$route_no )
        map <- addPolylines(map, data = subdivisions, fill = TRUE, fillColor = "grey")
        map <- addMarkers(map, lat = latstart, lng = longstart , label = "Route_Begin" )
        map <- addMarkers(map, lat = latend, lng = longend, label = "Route_End")
         map <- addLabelOnlyMarkers(map, lng = -123.3656, lat = 48.4284, label = content, labelOptions = labelOptions(noHide = T))
       
         }else{
        
         map <- addPolylines(map,data = shapes)
       }
        
        
         
  })

      
      
      
      
      
      
      
      
      
      
      
 
}


shiny::shinyApp(ui = ui, server = server) 

```


#Raw code for get stop municiplities
bc_stops_shape <- read_sf("bus_stops.shp")
write.csv(bc_stops_shape, "bc_stops_shape.csv")



mun_shape <- read.csv("mun_shapes.csv")
nrow(mun_shape)
stops <- read.delim2("stops.txt", sep = ",", header = T)
stops = stops[, c("stop_id", "stop_code")]
head(stops)
stop_times <- read.delim2("stop_times.txt", sep = ",", header = T)
head(stop_times)
stop_times <- stop_times[, c("stop_id", "trip_id")]
trips <- read.delim2("trips.txt", sep = ",", header = T)
trips <- trips[, c("trip_id", "route_id")]
routes <- read.delim2("routes.txt", sep = ",", header = T)
routes <- routes[, c("route_id", "route_short_name")]
  


file <- merge(mun_shape, stops, by.x = "stopid", by.y = "stop_code", all.x = TRUE)
file <- merge(file, stop_times, by.x = "stop_id", by.y = "stop_id", all.x = TRUE)

file <- merge(file,trips, by.x = "trip_id", by.y = "trip_id", all.x = TRUE )
file <- merge(file, routes, by.x = "route_id", by.y = "route_id", all.x = TRUE)
file <- distinct(file, stop_id, .keep_all = TRUE)
write.csv(file, "file.csv")
head(file)
nrow(file)





